---
title: "Credit Risk Report"
author: "Risk Management"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
  html_document: default
fontsize: 8pt
documentclass: article
---
<!-- date: "`r format(Sys.time(), '%d %B, %Y')`" -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.path='Figs/', tidy = TRUE, fig.pos = 'H')
options(knitr.table.format = "latex")
```
\section{Relevant Portfolio Changes and Information}
```{r libraries, include=FALSE}
library(tidyverse)
library(magrittr)
library(purrr)
library(broom)
library(stringr)
library(knitr)
library(kableExtra)
library(cowplot)
library(formattable)
library(gridExtra)
```
```{r, echo = FALSE, message = FALSE}
# recrear datos y funciones de reporte_riesgo_credito.R
source(file = "reporte_riesgo_credito_simple.R")
```
```{r section1, comment='' ,  echo=FALSE, size = 'normalsize'}
section_sep <- unique(text_df$section)[1]
```
\subsubsection{`r section_sep`}
```{r parrafo_1, comment='' ,  echo=FALSE, size = 'normalsize', fig.pos="h"}
kable(text_df %>% 
        dplyr::filter(section == section_sep) %>% 
        dplyr::select(-c(line, section)),
      "latex", booktabs = T) %>% 
  kable_styling(latex_options = c("striped", "HOLD_position", "condensed"), position = "center", full_width = F, font_size = 8) %>% 
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "45em") %>% 
  row_spec(0, background = myColourT4, color = myColourT2, bold = T)
```
```{r section2, comment='' ,  echo=FALSE, size = 'normalsize'}
section_sep <- unique(text_df$section)[2]
```
\subsubsection{`r section_sep`}
```{r parrafo_2, comment='' ,  echo=FALSE, size = 'normalsize', fig.pos="h"}
kable(text_df %>% 
        dplyr::filter(section == section_sep) %>% 
        dplyr::select(-c(line, section)),
      "latex", booktabs = T) %>% 
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center",full_width = F, font_size = 8) %>% 
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "45em") %>% 
  row_spec(0, background = myColourT4, color = myColourT2, bold = T)
```
```{r section3, comment='' ,  echo=FALSE, size = 'normalsize'}
section_sep <- unique(text_df$section)[3]
```
\subsubsection{`r section_sep`}
```{r parrafo_3, comment='' ,  echo=FALSE, size = 'normalsize', fig.pos="h"}
kable(text_df %>% 
        dplyr::filter(section == section_sep) %>% 
        dplyr::select(-c(line, section)),
      "latex", booktabs = T) %>% 
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = F, font_size = 8) %>% 
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "45em") %>% 
  row_spec(0, background = myColourT4, color = myColourT2, bold = T)
```
\subsection{News}
```{r summary_news, comment='' ,  echo=FALSE, size = 'normalsize', fig.pos="h"}
kable(Rnews, "latex", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = F, font_size = 8)  %>%
  column_spec(1, border_right =F,  width = "3em") %>% 
  column_spec(2, border_right =F,  width = "48em")%>% 
  row_spec(0, background = myColourT4, color = myColourT2, bold = T)
```
<!-- \pagebreak -->

\section{Portfolio EDA}
\subsection{Default Probabilities}
\subsubsection{Moody's top 25 EDFs}
```{r EDF_PDet_head, comment='' ,  echo=FALSE, size = "normalsize", fig.pos="h"}
kable(cbind(EDF_head, PDet_head),"latex", booktabs = T, digits = 2, longtable = T) %>%
  add_header_above(c("","Default" = 4,"", "Deterioration" = 2)) %>%  
  kable_styling(latex_options=c("striped","HOLD_position","condensed", "repeat_header"), position="center", full_width=F, font_size=7) %>%
  column_spec(1, bold = T, border_right = T, width = "15em") %>%
  column_spec(2, width = "3.5em") %>%
  column_spec(3, width = "3.5em") %>%
  column_spec(4, width = "3.5em") %>%
  column_spec(5, width = "3.5em") %>%
  column_spec(6, bold = T, border_left = T, border_right = T, width = "15em") %>%
  column_spec(7, width = "3.5em") %>%
  column_spec(8, width = "3.5em") %>% 
  row_spec(0, background = myColourT4, color = myColourT2, bold = T)
```
```{r EDF_gg, echo=TRUE, fig.width=12, fig.height=4, fig.align="center", fig.pos="h"}
# plot_grid(gg_EDF_PDet ,gg_EDF_EDFLY, gg_PDet_PDetLY, align = "hv", rel_widths = c(1,1,1), scale = c(1.95,1.95,1.95), nrow = 1, axis = c("l","c","r"))
grid.arrange(gg_EDF_PDet ,gg_EDF_EDFLY, gg_PDet_PDetLY, nrow = 1)
```
\subsubsection{Price-Implicit Default Probabilities top 25}
```{r prtB_head, comment='' ,  echo=FALSE, size = "normalsize", fig.pos="h"}
kable(prtB_head,"latex", booktabs = T, digits = 4, longtable = T) %>%
  kable_styling(latex_options=c("striped","HOLD_position","condensed", "repeat_header"), position="center", full_width=F, font_size=8) %>%
  column_spec(1, bold = T, border_right = T, width = "15em") %>%
  column_spec(2, width = "7.5em") %>%
  column_spec(3, width = "7.5em") %>%
  column_spec(4, width = "5em") %>%
  row_spec(0, background = myColourT4, color = myColourT2, bold = T)
```
```{r heaven_and_hell, echo=TRUE, fig.width=8,fig.height=8, fig.align="center", fig.pos="h"}
gg_EDF_PD_p
```
\subsection{Risk Filter and Review Status}
```{r filter_head, comment='' ,  echo=FALSE, size = "normalsize", fig.pos="h"}
options(knitr.table.format = "latex")
names(tabla_filtro) <- names(tabla_filtro) %>% gsub(pattern="_", replacement = "")
tabla_filtro %>%
  dplyr::mutate(EBITNetDebt = EBITNetDebt %>% round(digits = 3),
                EBITprox12m = EBITprox12m %>% round(digits = 0),
                EBITultTrim = EBITultTrim %>% round(digits = 0)) %>% 
  dplyr::mutate(
    Commentary = ifelse(is.na(Commentary), "--", Commentary)
  ) %>% 
  dplyr::mutate(
    Issuer = cell_spec(Issuer,format =  "latex"),
    EBITNetDebt = cell_spec(EBITNetDebt,format =  "latex"),
    EBITprox12m = cell_spec(EBITprox12m,format =  "latex"),
    EBITultTrim = cell_spec(EBITultTrim,format =  "latex"),
    ReviewDate = cell_spec(ReviewDate,format =  "latex", 
                            color = ifelse(is.na(ReviewDate), myColourT2, myColourT1),
                            background = factor(is.na(ReviewDate), c(TRUE,FALSE), c(myColourT4, myColourT2))),
    Commentary = cell_spec(Commentary,format =  "latex",
                           color = ifelse(Commentary == "+", myColour3, myColourT1),
                           background = ifelse(Commentary == "x", myColour6, myColourT2))
    ) %>%
  dplyr::select(Issuer, EBITNetDebt, EBITprox12m, EBITultTrim, ReviewDate, Commentary) %>% 
  kable(format = "latex", booktabs = T,  longtable = T, escape = F, digits = 3) %>%
  kable_styling(latex_options=c("striped","HOLD_position","condensed", "repeat_header"), position="center", full_width=F, font_size=8) %>%
  column_spec(1, bold = T, border_right = T, width = "15em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "6em") %>%
  column_spec(4, width = "6em") %>%
  column_spec(5, width = "6em") %>%
  column_spec(6, width = "6em") %>%  
  row_spec(0, background = myColourT4, color = myColourT2, bold = T)
```
\subsection{Market Value}
```{r sector_gg, echo=TRUE, fig.width=10, fig.height=10, fig.align="center", fig.pos="h"}
plot_grid(gg_Mkt_Country,gg_Mkt_Sector, gg_Mkt_Mat, align = "h", rel_widths = c(1,1,1), scale = c(1,1,1))
```
\subsubsection{Expected Loss}
```{r ExpLoss, comment='' ,  echo=FALSE, size = 'normalsize', fig.pos="h"}
kable(prt_EL %>% 
        dplyr::mutate(Market_Value = formattable::currency(MktValue, digits = 2),
                      Expected_Loss = formattable::currency(ExpectedLoss_MktV, digits = 2),
                      Percent_EL = formattable::percent(PercExpectedLoss, digits = 4)) %>% 
        dplyr::select(ReportingAccountName, Market_Value, Expected_Loss, Percent_EL), "latex", booktabs = T) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "center", full_width = F, font_size = 8)  %>%
  column_spec(1, border_right =T,  width = "15em", bold = T) %>% 
  column_spec(2, border_right =F,  width = "10em")%>%
  column_spec(3, border_right =F,  width = "10em")%>%
  column_spec(4, border_right =F,  width = "10em")%>%
  row_spec(0, background = myColourT4, color = myColourT2, bold = T)
```


